Forecasting Influenza Hospitalizations Using a Bayesian Hierarchical Nonlinear Model with Discrepancy

### 2025-08-14 response.tex

``Figure 6 helps
illustrate why this modeling decision was made.
The figure shows scatterplots of ILI percentage and 
hospitalizations on the top row.
The bottom row shows scatterplots of the difference between hospitalizations and 
1 week 
lags
by ILI percentage at the US national level. The plots in the right column
are of the logarithm of hospitalizations. The lines through the points are
drawn by connecting hospitalizations for consecutive weeks during the flu 
season.
These plots show that a linear or quadratic relationship between ILI percentage 
and hospitalizations does not capture much of the temporal correlation in 
hospitalizations as shown by the obvious loops drawn in the plot. 
However, when including a 
single AR lag of hospitalizations in the model, much of the time 
correlation is
accounted for as shown by the tighter and more frequent crossing of lines
in the bottom row. Models with more than 1 AR lag showed little or no 
improvement over 1 lag."}

\item The authors provide also state level predictions. However, I do not see 
where a spatial component is included in the model. Is this only via P or are 
all states just modelled independently. For influenza I would think that it 
might be reasonable to assume that neighbouring states show similar behaviour 
in both ILI and hosptialisation so that borrowing strength between states 
within one model seems sensible. Please discuss.

\spencer{Yes, borrowing strength between states would be reasonable, but 
fitting such a model would likely take much more time than was give by FluSight
to produce forecasts. In the revised manuscript, after defining the ILI model
we state:

``Model (\ref{eq:ili_model}) was fit 
independently for each location. This decision was made largely due to the 
limited time given by FluSight to produce forecasts. That is,
during the competition, data were typically released on Wednesday afternoons and
forecasts were due by the evening of the same day giving only a few hours to 
produce forecasts. A natural extension of the model would be to allow for states
to borrow information from neighboring states."

We also added the following to the discussion:

``The models in this manuscript were such that the data in each
location were modeled as
independent from all other locations. It is reasonable to assume that a
disease outbreak in one state will share characterstics with the outbreak in 
neighboring states, and indeed the behavior of ILI and hospitalizations is more
closely related for neighboring states as shown in data plots in the
supplementary materials. The one 2023 FluSight forecast model which outperformed
the ASGD\_NORM2, the UGA\_flucast-INFLAenza, was listed as being a spatial
model. And in past seasons, some of the top performing forecast models also 
explicitly modeled spatial relationships."}

### 2025-08-14 manuscript_res.tex
editing almost complete

For the
remainder of this section, focus will be made on forecasts made by coupling the
ASGD and SIRD models with the 
normal hospitalization model where ILI is a quadratic predictor.
These forecast schemes are denoted as ASGD\_NORM2 and SIRD\_NOMR2. 
In the supplementary materials, we include analysis of 2023 hospitalization
forecasts for several other forecast
models including ASG, SIRD, SIR ILI models coupled with other variations of the
hospitalization model where the ASGD\_NORM2 and SIRD\_NORM2 models
showed the best and second best results respectively.

@@

    % \centering
    \begin{adjustwidth}{-1.2cm}{-1.5cm}
    \includegraphics[scale = .54]{Images/lwis_cover_sum.png}
    \caption{a) Averaged over location and horizon log-weighted interval score
    (LWIS) for each week during the season for the 21 models being compared. 
    Each grey line represents one model, but the ASGD\_NORM2 (blue) and 
    FluSight-baseline (red) are colored to stand out.
    b) Boxplots of all LWIS scores for 1, 2, 3, and 4-week ahead horizons 
    for the ASGD\_NORM2 (blue) and FluSight-baseline (red) models.
    c) Plot of empirical coverage against theoretical coverage for 11 
    predictive intervals from the 10\% nominal level to the 98\%. The black
    line $x = y$ shows where optimal coverage would fall.
    Each grey line represents one model, but the ASGD\_NORM2 (blue) and 
    FluSight-baseline (red) are colored to stand out.}
    \end{adjustwidth}
    \label{fig:lwis_cover_sum}
\end{figure}

@@

\begin{figure}[hbt!]
\begin{adjustwidth}{-1.2cm}{-1.5cm}
    % \begin{minipage}{\linewidth}
    \centering
    \makebox[\linewidth][l]{
    \includegraphics[scale = .5]{Images/state_and_date_lwis.png}
    }
    \end{adjustwidth}
    \caption{Ratio of average log-weighted interval score (LWIS) for ASGD\_NORM2 
    to that of on competing FluSight model. Scores are averaged
    over all targets within indicated location (top) or week (bottom) and 
    only include forecasts shared by both models. Lower scores (blue) indicate
    superior performance by the ASGD\_NORM2 model and higher scores (red)
    indicate superior performance by competing model.}
    \label{fig:state_and_date_lwis}
    % \end{minipage}

>>>>

For the
remainder of this section, focus will be made on forecasts made by coupling the
ASGD and SIRD models with the 
normal hospitalization model where ILI is a quadratic predictor.
These forecast schemes are denoted as ASGD\_NORM2 and SIRD\_NOMR2. 
In the supplementary materials, we include analysis of 2023 hospitalization
forecasts for several other forecast
models including ASG, SIRD, SIR ILI models coupled with other variations of the
hospitalization model where the ASGD\_NORM2 showed the best results
and the SIRD\_NORM2 performed nearly as well.

@@

    % \centering
    \begin{adjustwidth}{-1.2cm}{-1.5cm}
    \includegraphics[scale = .54]{Images/lwis_cover_sum.png}
    \caption{a) Averaged over location and horizon log-weighted interval score
    (LWIS) for each week during the season for the 21 models being compared. 
    Each grey line represents one model, but the ASGD\_NORM2 (blue), 
    SIRD\_NORM2 (green), and 
    FluSight-baseline (red) are colored to stand out.
    b) Boxplots of all LWIS scores for 1, 2, 3, and 4-week ahead horizons 
    for the ASGD\_NORM2 (blue) and FluSight-baseline (red) models.
    c) Plot of empirical coverage against theoretical coverage for 11 
    predictive intervals from the 10\% nominal level to the 98\%. The black
    line $x = y$ shows where optimal coverage would fall.
    Each grey line represents one model, but the ASGD\_NORM2 (blue) and 
    FluSight-baseline (red) are colored to stand out.}
    \end{adjustwidth}
    \label{fig:lwis_cover_sum}
\end{figure}

@@

\begin{figure}[hbt!]
\begin{adjustwidth}{-1.2cm}{-1.5cm}
    % \begin{minipage}{\linewidth}
    \centering
    \makebox[\linewidth][l]{
    \includegraphics[scale = .5]{Images/state_and_date_lwis.png}
    }
    \end{adjustwidth}
    \caption{Ratio of average log-weighted interval score (LWIS) for ASGD\_NORM2 
    to that of each competing FluSight model. Scores are averaged
    over all targets within indicated location (top) or week (bottom) and 
    only include forecasts shared by both models. Lower scores (blue) indicate
    superior performance by the ASGD\_NORM2 model and higher scores (red)
    indicate superior performance by competing model.}
    \label{fig:state_and_date_lwis}
    % \end{minipage}

### 2025-08-14 supplemental_res.tex
editing almost complete

    % \centering
    \begin{adjustwidth}{-1.2cm}{-1.5cm}
    \includegraphics[scale = .54]{Images/wis_cover_sum.png}
    \caption{a) Averaged over location and horizon weighted interval score
    (WIS) for each week during the season for the 21 models being compared. 
    Each grey line represents one model, but the ASGD\_NORM2 (blue) and 
    FluSight-baseline (red) are colored to stand out.
    b) Boxplots of all WIS scores for 1, 2, 3, and 4-week ahead horizons 
    for the ASGD\_NORM2 (blue) and FluSight-baseline (red) models. 
    To improve vizualization, the $y$-axis
    is on the log scale.}
    \end{adjustwidth}
    \label{fig:wis_cover_sum}
\end{figure}

\begin{figure}[hbt!]
\begin{adjustwidth}{-1.2cm}{-1.5cm}
    % \begin{minipage}{\linewidth}
    \centering
    \makebox[\linewidth][l]{
    \includegraphics[scale = .5]{Images/state_and_date_wis.png}
    }
    \end{adjustwidth}
    \caption{Ratio of average weighted interval score (WIS) for ASGD\_NORM2 
    to that of on competing FluSight model. Scores are averaged
    over all targets within indicated location (top) or week (bottom) and 
    only include forecasts shared by both models. Lower scores (blue) indicate
    superior performance by the ASGD\_NORM2 model and higher scores (red)
    indicate superior performance by competing model.}
    \label{fig:state_and_date_wis}
    % \end{minipage}

>>>>

    % \centering
    \begin{adjustwidth}{-1.2cm}{-1.5cm}
    \includegraphics[scale = .54]{Images/wis_cover_sum.png}
    \caption{a) Averaged over location and horizon weighted interval score
    (WIS) for each week during the season for the 21 models being compared. 
    Each grey line represents one model, but the ASGD\_NORM2 (blue),
    SIRD\_NORM2 (green), and 
    FluSight-baseline (red) are colored to stand out.
    b) Boxplots of all WIS scores for 1, 2, 3, and 4-week ahead horizons 
    for the ASGD\_NORM2 (blue) and FluSight-baseline (red) models. 
    To improve vizualization, the $y$-axis
    is on the log scale.}
    \end{adjustwidth}
    \label{fig:wis_cover_sum}
\end{figure}

\begin{figure}[hbt!]
\begin{adjustwidth}{-1.2cm}{-1.5cm}
    % \begin{minipage}{\linewidth}
    \centering
    \makebox[\linewidth][l]{
    \includegraphics[scale = .5]{Images/state_and_date_wis.png}
    }
    \end{adjustwidth}
    \caption{Ratio of average weighted interval score (WIS) for ASGD\_NORM2 
    to that of each competing FluSight model. Scores are averaged
    over all targets within indicated location (top) or week (bottom) and 
    only include forecasts shared by both models. Lower scores (blue) indicate
    superior performance by the ASGD\_NORM2 model and higher scores (red)
    indicate superior performance by competing model.}
    \label{fig:state_and_date_wis}
    % \end{minipage}
